### 2021-03-04 background.tex
revision for jounal - background - result

Google Play Store is the primary market source for Android apps, and has a flexible policy regarding the process of publishing apps. Therefore, every month many Android apps are cleared from it because of issues related to spyware and other types of malware \cite{DBLP:conf/msr/WangLL0X18}. For security reasons, Google play list each app with the requested permission. However, many malicious apps usually request more permissions than their APIs normally would require~\cite{DBLP:conf/ccs/FeltCHSW11}. Those permissions are presented to the user during the installation of a new app, since Android version 6, but most of the users are careless since they just want the end product \kn{Is there some citation or blog entry atleast that has shown this to be the real case with users?}.

Nowadays, malware becomes more stealthy and hackers learn how to avoid anti-virus signature checks, by obfuscating the native code \kn{Here we should cite the work of String hound (https://dl.acm.org/doi/10.1145/3320269.3384745)}, calling java libraries, or even by creating root exploits, since the native code is allowed to directly make syscalls. Another approach to rooting is making a side attack aimed at a benign app to make a syscall, exploiting its native code to get root access. Those are kind of attack that usually tackled with the Android Mining Sandbox \cite{DBLP:conf/icse/JamrozikSZ16}.

@@

\kn{Please write one sentence here saying why test generation tools could solve the problem, and then list the related work. The term test generation comes out out nowhere.} Regarding test generating tools used for mining Sandboxes, Jamrozik et al \cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps. Li e tal.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy. In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} regarding malware analysis, and showed that Droidbot is able to trigger an amount of sensitive behaviors, like data leaks and file accesses, higher than Monkey. From the same authors, another test generator tool for Android, described as Humanoid \cite{DBLP:conf/kbse/LiY0C19}, is a Droidbot evolution and presents a proposal that can generate humans like tests inputs, using deep learning.

>>>>

Google Play Store is the primary market source for Android apps, and has a flexible policy regarding the process of publishing apps. Therefore, every month many Android apps are cleared from it because of issues related to spyware and other types of malware \cite{DBLP:conf/msr/WangLL0X18}. For security reasons, Google play list each app with the requested permission. However, many malicious apps usually request more permissions than their APIs normally would require~\cite{DBLP:conf/ccs/FeltCHSW11}. Those permissions are presented to the user during the installation of a new app, since Android version 6, but most of the users are careless since they just want the end product.~\cite{DBLP:conf/soups/FeltHEHCW12} 
%\kn{Is there some citation or blog entry atleast that has shown this to be the real case with users?}

Nowadays, malware becomes more stealthy and hackers learn how to avoid anti-virus signature checks, by obfuscating the native code~\cite{DBLP:journals/corr/abs-2002-04540}
%\kn{Here we should cite the work of String hound (https://dl.acm.org/doi/10.1145/3320269.3384745)}
, calling java libraries, or even by creating root exploits, since the native code is allowed to directly make syscalls. Another approach to rooting is making a side attack aimed at a benign app to make a syscall, exploiting its native code to get root access. Those are kind of attack that usually tackled with the Android Mining Sandbox \cite{DBLP:conf/icse/JamrozikSZ16}.

@@

%\kn{Please write one sentence here saying why test generation tools could solve the problem, and then list the related work. The term test generation comes out out nowhere.} 
The main purpose of test generation tool is to find bugs. However, it also can be used to explore program behavior, and thus assist in the task of building Sandboxes. Regarding test generating tools used for mining Sandboxes, Jamrozik et al ~\cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps. Li e tal.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy. In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} regarding malware analysis, and showed that Droidbot is able to trigger an amount of sensitive behaviors, like data leaks and file accesses, higher than Monkey. From the same authors, another test generator tool for Android, described as Humanoid \cite{DBLP:conf/kbse/LiY0C19}, is a Droidbot evolution and presents a proposal that can generate humans like tests inputs, using deep learning.

### 2021-03-04 results.tex
revision for jounal - background - result

\kn{The following ssentence is kind of stating the obviouss and comes off as an attack already. THis should bee a conclusion box. Did we introduce joke in study? If not please introduce. If yes, please use joke by saying "joke, our ..... improves its performance by"}
Note that, in the \blls, the authors do not present a
discussion about the influence of DroidFax in the results, even
though here we report that the impact of DroidFax in the results is significant, ranging
from 16.44\% (DroidBot) to 51.79\% (Humanoid)---discarding our
\joke tool for which DroidFax improves its performance by 100\%. This result is
expected, since the \joke tool does not execute any dynamic analysis.
Next we discuss the result of each individual test generation tool.

@@

  \item[\joke] is our fake test case generation tool that help us understand the performance of the DroidFax static analysis algorithm for mining sandboxes. \kn{joke seems to be defined here but used before}
    We integrated \joke into the DroidXP benchmark as an additional test case generation tool that does not run the Android apps during the benchmark execution.
    As a result, the analysis using \joke reveals the performance of DroidFax static analysis algorithms alone. For the first execution, with the DroidFax static
    algorithms enabled, even though \joke does not execute the Android apps, its resulting sandbox detected 43.75\% of the malwares. For the second execution,
    that is, disabling the DroidFax static analysis algorithm, the resulting \joke sandbox was not able to detect any malware. This result
    was expected, since \joke does not analyze the Android apps during the benchmark execution.

@@

The DroidBot and Humanoid sandboxes detected the malicious version of the app \texttt{com.andoop.flyracing}. In this particular case, the malicious version changed the Android Manifest file, adding permissions to receive and send SMS messages
(Listing~\ref{lst:androidManifest}). With these permissions, malicious apps may get money fraudulently by sending messages without user confirmation, or may monitor messages or delete them without showing them to user. \kn{Is this the only app where the manifest was changed. If yes, I am not sure we can make broad claims about manifest being a serious place of vulnerabilities.} Moreover, after decompiling this malware, we also observed that the malicious version of the
\texttt{MainService} class introduced a
behavior that collects sensitive information (the International Mobile
Equipment Identity, IMEI) and sends it using an SMS message
(Listing~\ref{lst:mainService}).

@@

Now its an interesting case, because none of the computed sandboxes detected the malicious version of the app \texttt{com.andoop.flyracing}. Indeed, the malicious version only changes the Android Manifest file, modifying the meta-data \texttt{ADMOB\_PUBLISHER\_ID}. However, the AdMob is a monetization service provided by Google, and changing the AdMob \emph{publisher identifier} account redirects the advertisement's revenue to another destination.

@@

We also observed that the malicious version of the \texttt{d} class, indeed introduced a method \texttt{a}, that collects network and wifi information, like Mac address and network state. (Listing~\ref{lst:d})

@@

Our last example is from malicious version app \texttt{ru.qixi.android.smartrabbits}. It also was detected by all computed sandboxes, and such as the previous malware example, it changed the Android Manifest file, adding this time, permission to access fine location sources. This permission allows access location sources, such as the Global Positioning System (GPS) on the phone, where available. Malicious applications can use this resource to determine where the phone user are, and may consume additional battery power. (Listing~\ref{lst:androidManifest3})

@@

This malicious app clandestinely monitors the geographic location user and sink these information. The code that follows, show how the method \texttt{c}, from \texttt{q} class, collects these sensitive resource. (Listing~\ref{lst:c}).

@@

In this second study we used a tainted analysis approach to mine differences between the benign and malicious versions of each of the 96 Android apps in our dataset. To this end we leverage the FlowDroid\kn{ Have we cited flowdroid before. If yes, ignore my comment} tool, which tracks how sensitive information flows through the apps using tainted analysis algorithms. Regarding accuracy, the tainted analysis approach detected $58$ out of the $96$ pairs in our dataset ($60,42$\%), that is, the FlowDroid approach leads to a better performance than any sandbox originated in the second execution of the dynamic analysis tools (without the DroidFax static analysis algorithms).

>>>>

\kn{The following ssentence is kind of stating the obviouss and comes off as an attack already. THis should bee a conclusion box. Did we introduce joke in study? If not please introduce. If yes, please use joke by saying "joke, our ..... improves its performance by"}
Note that, in the \blls, the authors do not present a
discussion about the influence of DroidFax in the results, even
though here we report that the impact of DroidFax in the results is significant, ranging
from 16.44\% (DroidBot) to 51.79\% (Humanoid)---discarding our
\joke tool, the fake tool that does not execute apps during a benchmark execution, for which DroidFax improves its performance by 100\%. This result is
expected, since the \joke tool does not execute any dynamic analysis.
Next we discuss the result of each individual test generation tool.

@@

  \item[\joke] is our fake test case generation tool that help us understand the performance of the DroidFax static analysis algorithm for mining sandboxes. 
  %\kn{joke seems to be defined here but used before}
    We integrated \joke into the DroidXP benchmark as an additional test case generation tool that does not run the Android apps.
    As a result, the analysis using \joke reveals the performance of DroidFax static analysis algorithms alone. For the first execution, with the DroidFax static
    algorithms enabled, even though \joke does not execute the Android apps, its resulting sandbox detected 43.75\% of the malwares. For the second execution,
    that is, disabling the DroidFax static analysis algorithm, the resulting \joke sandbox was not able to detect any malware. This result
    was expected, since \joke does not analyze the Android apps during the benchmark execution.

@@

The DroidBot and Humanoid sandboxes detected the malicious version of the app \texttt{com.andoop.flyracing}. In this particular case, the malicious version changed the Android Manifest file, adding permissions to receive and send SMS messages
(Listing~\ref{lst:androidManifest}). With these permissions, malicious apps may get money fraudulently by sending messages without user confirmation, or may monitor messages or delete them without showing them to user. 
%\kn{Is this the only app where the manifest was changed. If yes, I am not sure we can make broad claims about manifest being a serious place of vulnerabilities.} 
Moreover, after decompiling this malware, we also observed that the malicious version of the
\texttt{MainService} class introduced a
behavior that collects sensitive information (the International Mobile
Equipment Identity, IMEI) and sends it using an SMS message
(Listing~\ref{lst:mainService}).

@@

Now we show an interesting case, because none of the computed sandboxes detected the malicious version of the app \texttt{com.andoop.flyracing}. Indeed, the malicious version only changes the Android Manifest file, modifying the meta-data \texttt{ADMOB\_PUBLISHER\_ID}. However, the AdMob is a monetization service provided by Google, and changing the AdMob \emph{publisher identifier} account redirects the advertisement's revenue to another destination.

@@

We also observed that the malicious version of the \texttt{d} class, introduced a method \texttt{a}, that collects network and wifi information, like Mac address and network state. (Listing~\ref{lst:d})

@@

Our last example is a malicious version app \texttt{ru.qixi.android.smartrabbits}. It also was detected by all computed sandboxes, and such as the previous malware example, it changed the Android Manifest file, adding this time, permission to access location sources. This permission allows access location sources, such as the Global Positioning System (GPS) on the phone, where available. Malicious applications can use this resource to determine where the phone user are, and may consume additional battery power. (Listing~\ref{lst:androidManifest3})

@@

This malicious app clandestinely monitors the geographic location user and sink these information to a web server. The code that follows, show how the method \texttt{c}, from \texttt{q} class, collects these sensitive resource. (Listing~\ref{lst:c}).

@@

In this second study we used a tainted analysis approach to mine differences between the benign and malicious versions of each of the 96 Android apps in our dataset. To this end we leverage the FlowDroid
%\kn{ Have we cited flowdroid before. If yes, ignore my comment} 
tool, which tracks how sensitive information flows through the apps using tainted analysis algorithms. Regarding accuracy, the tainted analysis approach detected $58$ out of the $96$ pairs in our dataset ($60,42$\%), that is, the FlowDroid approach leads to a better performance than any sandbox originated in the second execution of the dynamic analysis tools (without the DroidFax static analysis algorithms).
